SBML L3 paper response to reviewers

### 2020-01-02 main.tex
More answers

\textbf{\textit{1. When/why is standardization beneficial?}}

@@

These are important issues indeed.  In the revised manuscript, we have added text in the section titled ``Forthcoming challenges'' to acknowledge and touch upon some of the costs and benefits.  We feel that a more extended discussion of these topics have to be considered beyond the scope of this paper; notwithstanding this, we hope the new changes are enough to address the point to a reasonable extent.

@@

>>>>

\textbf{\textit{When/why is standardization beneficial? Interchange standards such as SBML become necessary only when i) there are already multiple competing formats/tools and ii) interoperation between these tools is desirable. A new tool defining its own format in a niche area may itself become the de facto standard for that subfield, independent of the HARMONY/COMBINE/SBML community and process. This is probably the norm in computational biology and is, in and of itself, not a bad thing. Challenges arise only when multiple groups develop tools independently, they cannot interoperate, and interoperability is necessary or desirable. It would help with the framing of the article if the authors addressed the criteria for language standardization explicitly early on. For example, in the context of the descriptions of the Level 3 extensions, it is not immediately clear to the reader why the qualitative modeling field required an SBML standard (instead of just using tool-specific formats); later this becomes (implicitly) apparent on page 13 line 40 when the authors note the need for CellNOpt to interoperate with GINsim (the example of model exchange between Simmune and BioNetGen also makes this point)}}

% We have added a some additional text in the ``Introduction'' and ``Impact of SBML'' sections about the general benefits of reproducibility, and advantages of persistent storage

@@

These are important issues indeed.  In the revised manuscript, we have added text in the section titled ``Forthcoming challenges'' to acknowledge and touch upon some of the costs and benefits.  We feel that a more extended discussion of these topics have to be considered beyond the scope of this paper, but we hope that the new changes are enough to address the point to a reasonable extent.

@@

These are interesting points.  However, we feel we cannot adequately expand on these issues in this article, both due to space limitations and time limitations, so we have removed the problematic statements to avoid potentially misleading claims.
